Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-21 sections/eval.tex
Update on Overleaf.

\subsubsection{Tensor Formats}
\willow{could this be a table?} We tested with both the row-major and the column-major implementations (labeled with a "R" and "C", respectively, where applicable in Figure \ref{spmv_grouped}) with Finch. Column-major SpMV consistently performs better than row-major SpMV (an average of 1.36x better) in TACO so we use column-major SpMV in TACO as our baseline.

\begin{table}[htbp]
    \centering
    \label{tensor_formats}
    \caption{SpMV Tensor Formats}
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Outer Level} & \textbf{Inner Level} & \textbf{Scalar Values} & \textbf{Style of Matrix}\\
        \hline
        \multirow{6}{*}{Dense} & \multirow{2}{*}{SparseList} & Element & sparse, real-valued matrices \\
        \cline{3-4} 
        & & Pattern & sparse, boolean-valued matrices \\
        \cline{2-4} 
        & SparseVBL & Element & real-valued matrices with blocked structure \\
        \cline{2-4}
        & SparseBand & Element & real-valued matrices with diagonal band \\
        \cline{2-4}
        & \multirow{2}{*}{SparsePoint} & Element & real-valued matrices with one value per row \\
        \cline{3-4} 
        & & Pattern & matrix with runs of true or false \\
        \hline 
    \end{tabular}

>>>>

\subsubsection{Tensor Formats}
For the tensor formats in Table \ref{spmv_tensor_formats}, we tested with both the row-major and the column-major implementations (labeled with a "R" and "C", respectively, where applicable in Figure \ref{spmv_grouped}) with Finch. Column-major SpMV consistently performs better than row-major SpMV (an average of 1.36x better) in TACO so we use column-major SpMV in TACO as our baseline.

\begin{table}[htbp]
    \centering
    \label{spmv_tensor_formats}
    \caption{SpMV Tensor Formats}
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Outer Level} & \textbf{Inner Level} & \textbf{Scalar Values} & \textbf{Style of Matrix}\\
        \hline
        \multirow{6}{*}{Dense} & \multirow{2}{*}{SparseList} & Element & sparse, real-valued matrices \\
        \cline{3-4} 
        & & Pattern & sparse, boolean-valued matrices \\
        \cline{2-4} 
        & SparseVBL & Element & real-valued matrices with blocked structure \\
        \cline{2-4}
        & SparseBand & Element & real-valued matrices with diagonal band \\
        \cline{2-4}
        & \multirow{2}{*}{SparsePoint} & Element & real-valued matrices with one value per row \\
        \cline{3-4} 
        & & Pattern & matrix with runs of true or false \\
        \hline 
    \end{tabular}
